Handling String-Number Conversion in String Constraint Solving

### 2019-11-08 draft.tex
don't know

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {L(A')}$ such that 
$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.

@@

The synchronisation formula is the conjunction 
$$
\syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
$$
The correctness of this construction is expressed by the following lemma
%\begin{lemma}
%For $\pim:\pvarone\rightarrow \nat$, $\pim':\pvartwo \rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
%we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof {\syncfof A {A'}}$ if and only if $\decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')$.
%\end{lemma}

\begin{lemma}
 $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
\end{lemma}

We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?

>>>>

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.

@@

The synchronisation formula is the conjunction 
$$\label{lemma:synccorrect}
\syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
$$
The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. Informally,
the

\begin{lemma}
 $\semof {\exists .\,\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
\end{lemma}

%We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?
%\begin{lemma}
%For $\pim:\pvarone\rightarrow \nat$, $\pim':\pvartwo \rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
%we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof {\syncfof A {A'}}$ if and only if $\decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')$.
%\end{lemma}

\lh{TODO: put this somewhere and explain}
